---
title       : Car Mileage Calculator
subtitle    : Pitch Presentation
author      : Peter Adam
job         : Data Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]    # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Project Aim and Development

People want to know what their cars mileage is, and how that ranks against other
cars.

This project aimed to build an application where a user can easily select the
make and model of their car and see how it compares to the competition.

The `mtcars` dataset includes mileage information on 32 cars, and this was the
basis for the development of the app.

The `radioButtons()` function was used for the manufacturer list, and then
a series of radioButtons were embedded within `conditionalPanel()` functions, so
that the options for model would appear per manufacturer selection.

---

## Project Development (cont.)

Individual model mileage numbers were taken out of R using `[n,1]` where `n` is
the car being selected. For example, the Cadillac Fleetwood:
``` {r}
    row.names(mtcars[15,0])
    mtcars[15,1]
```

The average was computed using `mean()`:

``` {r}
    mean(mtcars$mpg)
```

---

## Final Product

The final product is hosted at: https://padam0.shinyapps.io/shinyApp/
The raw files are hosted at: https://github.com/Padam-0/shinyApp

<img src = './assets/img/SS.jpg' height = 400></img>

--- &radio

## Feedback:
What did you think of this pitch?

1. _Good!_
2. Bad :(

*** .hint
Be nice!

*** .explanation
Aw, I'm sorry you feel that way!

